---
title: "Stability_analysis_fake_y_10_paper"
output: html_document
---

In this script, 
- the stabilty study is made for 10 different outcomes y
- At each iteration, the selection is made using the 749 genes and a subset of patients a 100 times. The subset of patients is determined using a 10-fold cross validation 10 times
- We compare the results for the KO framework (q = 0.2, q = 0.5), KOPI (q = 0.2, q= 0.5), the LASSO where lambda is chosen by cross validation, and tha LASSO with lambda oracle
- Results are aggregated into one histogram representing features selection frequencies.
_ We also use results table to compute informative metrics (table in the paper)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load sources and files }
source("/home/julie/Documents/Paper_codes/CRUKPAP_EXPERIMENTS/Stability/Settings.R")
source("/home/julie/Documents/Paper_codes/CRUKPAP_EXPERIMENTS/Stability/Functions.R")

```


```{r Aggregation of the results obtained over the ten iterations}
y.rep <- 10
beta.tot <- c()
table.selected.genes.LPLR.tot <- data.frame()
table.selected.genes.LPLR.oracle.tot <- data.frame()

table.selected_genes.KOPI_0.1.tot <- data.frame()
table.selected_genes.KOPI_0.2.tot <- data.frame()
table.selected_genes.KOPI_0.3.tot <- data.frame()
table.selected_genes.KOPI_0.5.tot <- data.frame()

table.selected_genes.Vanilla_0.1.tot <- data.frame()
table.selected_genes.Vanilla_0.2.tot <- data.frame()
table.selected_genes.Vanilla_0.3.tot <- data.frame()
table.selected_genes.Vanilla_0.5.tot <- data.frame()

data_analysis <- data.frame()

for (rep in 1:y.rep){
  print(rep)
  # load selected features for all methods 
  
  load(str_glue("/home/julie/Documents/Paper_codes/CRUKPAP_EXPERIMENTS/Stability/R_files/y_rep/table.selected_genes_cv_Vanilla_",rep,".R"))
  load(str_glue("/home/julie/Documents/Paper_codes/CRUKPAP_EXPERIMENTS/Stability/R_files/y_rep/table.selected_genes_cv_KOPI_",rep,".R"))
  load(str_glue("/home/julie/Documents/Paper_codes/CRUKPAP_EXPERIMENTS/Stability/R_files/y_rep/table_selected_genes_LPLR_",rep,".R"))
  load(str_glue("/home/julie/Documents/Paper_codes/CRUKPAP_EXPERIMENTS/Stability/R_files/y_rep/table_selected_genes_LPLR_oracle_",rep,".R"))
  
   # Save beta used at each iteration
  beta.tot <- c(beta.tot, beta)
  
  # Merged results
  table.selected.genes.LPLR.tot <- rbind(table.selected.genes.LPLR.tot, table.selected.genes.LPLR)
  table.selected.genes.LPLR.oracle.tot <- rbind(table.selected.genes.LPLR.oracle.tot, table.selected.genes.LPLR.oracle)
   
  table.selected_genes.Vanilla_0.1.tot <- rbind(table.selected_genes.Vanilla_0.1.tot, table.selected_genes.Vanilla_0.1)
  table.selected_genes.Vanilla_0.2.tot <- rbind(table.selected_genes.Vanilla_0.2.tot, table.selected_genes.Vanilla_0.2)
  table.selected_genes.Vanilla_0.3.tot <- rbind(table.selected_genes.Vanilla_0.3.tot, table.selected_genes.Vanilla_0.3)
  table.selected_genes.Vanilla_0.5.tot <- rbind(table.selected_genes.Vanilla_0.5.tot, table.selected_genes.Vanilla_0.5)
  
  table.selected_genes.KOPI_0.1.tot <- rbind(table.selected_genes.KOPI_0.1.tot, table.selected_genes.KOPI_0.1)
  table.selected_genes.KOPI_0.2.tot <- rbind(table.selected_genes.KOPI_0.2.tot, table.selected_genes.KOPI_0.2)
  table.selected_genes.KOPI_0.3.tot <- rbind(table.selected_genes.KOPI_0.3.tot, table.selected_genes.KOPI_0.3)
  table.selected_genes.KOPI_0.5.tot <- rbind(table.selected_genes.KOPI_0.5.tot, table.selected_genes.KOPI_0.5)
  
  
  # Feature selection metrics (used in the paper table)

 list_non_null = which(beta!=0)
  true_genes = rep("False discoveries ", ncol(X_real))
  true_genes[ which(beta!=0)] <- "True genes "
  bin_width <- 0.01
  
  prop_selection.genes_LPLR <- rowMeans(table.selected.genes.LPLR)
  prop_selection.genes_LPLR_0 <- prop_selection.genes_LPLR[ !prop_selection.genes_LPLR == 0]
  true_genes_LPLR_0 = true_genes[ !prop_selection.genes_LPLR == 0]

  df.genes <- data.frame(freq = prop_selection.genes_LPLR_0, status = as.factor(true_genes_LPLR_0))

  prop_selection.genes_LPLR_oracle <- rowMeans(table.selected.genes.LPLR.oracle)
  prop_selection.genes_LPLR_oracle_0 <- prop_selection.genes_LPLR_oracle[ !prop_selection.genes_LPLR_oracle == 0]
  true_genes_LPLR_oracle_0 <- true_genes[ !prop_selection.genes_LPLR_oracle == 0]

  df.genes.oracle <- data.frame(freq = prop_selection.genes_LPLR_oracle_0, status = as.factor(true_genes_LPLR_oracle_0))


  prop_selection_0.2 <- rowSums(table.selected_genes.KOPI_0.2)
  prop_selection_0.5 <- rowSums(table.selected_genes.KOPI_0.5)

  prop_selection_0.2_0 <- prop_selection_0.2[ !prop_selection_0.2 == 0]
  prop_selection_0.5_0 <- prop_selection_0.5[ !prop_selection_0.5 == 0]

  data_0.2_KOPI <- data.frame(freq = prop_selection_0.2_0/100, status = as.factor(true_genes[ !prop_selection_0.2 == 0]))
  data_0.5_KOPI <- data.frame(freq = prop_selection_0.5_0/100, status = as.factor(true_genes[ !prop_selection_0.5 == 0]))


  prop_selection_0.2 <- rowSums(table.selected_genes.Vanilla_0.2)
  prop_selection_0.5 <- rowSums(table.selected_genes.Vanilla_0.5)

  prop_selection_0.2_0 <- prop_selection_0.2[ !prop_selection_0.2 == 0]
  prop_selection_0.5_0 <- prop_selection_0.5[ !prop_selection_0.5 == 0]

  data_0.2 <- data.frame(freq = prop_selection_0.2_0/100, status = as.factor(true_genes[ !prop_selection_0.2 == 0]))
  data_0.5 <- data.frame(freq = prop_selection_0.5_0/100, status = as.factor(true_genes[ !prop_selection_0.5 == 0]))

 
  
  max.freq.LPLR <- max(df.genes$freq)
  max.freq.FD.LPLR <- nrow(df.genes[df.genes$freq == max.freq.LPLR & df.genes$status == "False discoveries ",])
  max.freq.TD.LPLR <- nrow(df.genes[df.genes$freq == max.freq.LPLR & df.genes$status == "True genes ",])

  
  max.freq.LPLR.oracle <- max(df.genes.oracle$freq)
  max.freq.FD.LPLR.oracle <- nrow(df.genes.oracle[df.genes.oracle$freq == max.freq.LPLR.oracle & df.genes.oracle$status == "False discoveries ",])
  max.freq.TD.LPLR.oracle <- nrow(df.genes.oracle[df.genes.oracle$freq == max.freq.LPLR.oracle & df.genes.oracle$status == "True genes ",])


  max.freq.KOPI_0.2 <- max(data_0.2_KOPI$freq)
  max.freq.FD.KOPI_0.2 <- nrow(data_0.2_KOPI[data_0.2_KOPI$freq == max.freq.KOPI_0.2 & data_0.2_KOPI$status == "False discoveries ",])
  max.freq.TD.KOPI_0.2 <- nrow(data_0.2_KOPI[data_0.2_KOPI$freq == max.freq.KOPI_0.2 & data_0.2_KOPI$status == "True genes ",])
  
  
  max.freq.KOPI_0.5 <- max(data_0.5_KOPI$freq)
  max.freq.FD.KOPI_0.5 <- nrow(data_0.5_KOPI[data_0.5_KOPI$freq == max.freq.KOPI_0.5 & data_0.5_KOPI$status == "False discoveries ",])
  max.freq.TD.KOPI_0.5 <- nrow(data_0.5_KOPI[data_0.5_KOPI$freq == max.freq.KOPI_0.5 & data_0.5_KOPI$status == "True genes ",])
  
  max.freq.KO_0.2 <- max(data_0.2$freq)
  max.freq.FD.KO_0.2 <- nrow(data_0.2[data_0.2$freq == max.freq.KO_0.2 & data_0.2$status == "False discoveries ",])
  max.freq.TD.KO_0.2 <- nrow(data_0.2[data_0.2$freq == max.freq.KO_0.2 & data_0.2$status == "True genes ",])
  
  max.freq.KO_0.5 <- max(data_0.5$freq)
  max.freq.FD.KO_0.5 <- nrow(data_0.5[data_0.5$freq == max.freq.KO_0.5 & data_0.5$status == "False discoveries ",])
  max.freq.TD.KO_0.5 <- nrow(data_0.5[data_0.5$freq == max.freq.KO_0.5 & data_0.5$status == "True genes ",])
  
  data_analysis_part <- data.frame(
    max.freq = c(max.freq.LPLR, max.freq.LPLR.oracle, max.freq.KO_0.2, max.freq.KO_0.5, max.freq.KOPI_0.2, max.freq.KOPI_0.5), 
    max.freq.FD = c(max.freq.FD.LPLR, max.freq.FD.LPLR.oracle, max.freq.FD.KO_0.2, max.freq.FD.KO_0.5, max.freq.FD.KOPI_0.2, max.freq.FD.KOPI_0.5), 
    max.freq.TD = c(max.freq.TD.LPLR, max.freq.TD.LPLR.oracle, max.freq.TD.KO_0.2, max.freq.TD.KO_0.5, max.freq.TD.KOPI_0.2, max.freq.TD.KOPI_0.5), 
    method = c("LPLR (lambda.min)", "LPLR (lambda.oracle)", "KO 0.2", "KO 0.5", "KOPI 0.2", "KOPI 0.5")) 
  
  data_analysis <- rbind(data_analysis, data_analysis_part)

  }
```


Sometimes there are error messages when no features is selected (max(numeric(o)))

### Final histograms

```{r Aggregated histograms with feature selection frequency accross the 10 iterations}

# The results are stacked which means that we treat the results as if there were 100 non null genes.

# get the non null beta for all iterations

list_non_null <- which(beta.tot!=0)
true_genes <- rep("False discoveries ", ncol(X_real)*y.rep)
true_genes[ which(beta.tot!=0)] <- "True genes "
bin_width <- 0.01

# get selection frequency 

# for the LASSO

prop_selection.genes_LPLR <- rowMeans(table.selected.genes.LPLR.tot)
prop_selection.genes_LPLR_0 <- prop_selection.genes_LPLR[ !prop_selection.genes_LPLR == 0]# Remove features that have never been selected
true_genes_LPLR_0 <- true_genes[ !prop_selection.genes_LPLR == 0]

df.genes <- data.frame(freq = prop_selection.genes_LPLR_0, status = as.factor(true_genes_LPLR_0))

max_bin_count_LPLR <- df.genes$freq %>% cut(breaks = seq(0, 1, by = bin_width), include.lowest = TRUE) %>% table() %>% max() # To adjust y-axis size

# for the oracle LASSO

prop_selection.genes_LPLR_oracle <- rowMeans(table.selected.genes.LPLR.oracle.tot)
prop_selection.genes_LPLR_oracle_0 <- prop_selection.genes_LPLR_oracle[ !prop_selection.genes_LPLR_oracle == 0]# Remove features that have never been selected
true_genes_LPLR_oracle_0 <- true_genes[ !prop_selection.genes_LPLR_oracle == 0]

df.genes.oracle <- data.frame(freq = prop_selection.genes_LPLR_oracle_0, status = as.factor(true_genes_LPLR_oracle_0))

max_bin_count_LPLR_oracle <- df.genes.oracle$freq %>% cut(breaks = seq(0, 1, by = bin_width), include.lowest = TRUE) %>% table() %>% max() # To adjust y-axis size

# For KOPI

prop_selection_0.2 <- rowSums(table.selected_genes.KOPI_0.2.tot)
prop_selection_0.5 = rowSums(table.selected_genes.KOPI_0.5.tot)

prop_selection_0.2_0 <- prop_selection_0.2[ !prop_selection_0.2 == 0]# Remove features that have never been selected
prop_selection_0.5_0 <- prop_selection_0.5[ !prop_selection_0.5 == 0]# Remove features that have never been selected

data_0.2_KOPI <- data.frame(freq = prop_selection_0.2_0/100, status = as.factor(true_genes[ !prop_selection_0.2 == 0]))
data_0.5_KOPI <- data.frame(freq = prop_selection_0.5_0/100, status = as.factor(true_genes[ !prop_selection_0.5 == 0]))

max_bin_count_KOPI_0.2 <- data_0.2_KOPI$freq %>% cut(breaks = seq(0, 1, by = bin_width), include.lowest = TRUE) %>% table() %>% max() # To adjust y-axis size
max_bin_count_KOPI_0.5 <- data_0.5_KOPI$freq %>% cut(breaks = seq(0, 1, by = bin_width), include.lowest = TRUE) %>% table() %>% max()# To adjust y-axis size

# For the KO framework

prop_selection_0.2 <- rowSums(table.selected_genes.Vanilla_0.2.tot)
prop_selection_0.5 <- rowSums(table.selected_genes.Vanilla_0.5.tot)

prop_selection_0.2_0 <- prop_selection_0.2[ !prop_selection_0.2 == 0]# Remove features that have never been selected
prop_selection_0.5_0 <- prop_selection_0.5[ !prop_selection_0.5 == 0]# Remove features that have never been selected

data_0.2 <- data.frame(freq = prop_selection_0.2_0/100, status = as.factor(true_genes[ !prop_selection_0.2 == 0]))
data_0.5 <- data.frame(freq = prop_selection_0.5_0/100, status = as.factor(true_genes[ !prop_selection_0.5 == 0]))

max_bin_count_KO_0.2 <- data_0.2$freq %>% cut(breaks = seq(0, 1, by = bin_width), include.lowest = TRUE) %>% table() %>% max()# To adjust y-axis size
max_bin_count_KO_0.5 <- data_0.5$freq %>% cut(breaks = seq(0, 1, by = bin_width), include.lowest = TRUE) %>% table() %>% max()# To adjust y-axis size

ylim.value <- max(max_bin_count_KO_0.2, max_bin_count_KO_0.5, max_bin_count_KOPI_0.5, max_bin_count_KOPI_0.2, max_bin_count_LPLR)

hist.genes <- ggplot(df.genes, aes(x = freq, fill = status)) +
  geom_histogram(binwidth = 0.01, color = "black") +
  #ylim(0, ylim.value) +
  labs(title = "Selection proportion of genes selected more than once",
       x = "Selection frequency",
       y = "Number of genes") +
  theme(axis.text.x = element_text(size = 26, face = "bold"),
        axis.title.x = element_text(size = 28),
        axis.title.y = element_text(size = 28),
        axis.text.y = element_text(size = 30, face = "bold"),
        plot.subtitle = element_text(hjust = 0),
        plot.caption = element_text(size = 22, face = "bold"),
        panel.background = element_rect(fill = "#F6F6F6"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"),
        plot.title = element_blank(),
        legend.position = c(0.5, 0.8),
        legend.text = element_text(size = 28),    
 legend.title = element_text(size = 28),
 plot.margin = unit(c(0.6, 0.2, 0.2, 0.6), "cm")
  ) +
  scale_fill_manual(
    values = c("#7c6fb0", "#FF5733", "#FFFF66"),
    name = expression("LASSO (" * lambda[min] * "), n = 2150")
  )
print(hist.genes)


TP_1_LPLR <- nrow(df.genes[df.genes$freq == 1 & df.genes$status == "True genes ", ])
FD_1_LPLR <- nrow(df.genes[df.genes$freq == 1 & df.genes$status == "False discoveries ", ])
nb_selected_LPLR <- nrow(df.genes)
prop_TD_LPLR <- 100*nrow(df.genes[df.genes$status == "True genes ",])/nb_selected_LPLR
TP_all_LPLR <- nrow(df.genes[df.genes$status == "True genes ", ])


hist.genes.oracle <- ggplot(df.genes.oracle, aes(x = freq, fill = status)) +
    geom_histogram(binwidth = 0.01, color = "black") +
    #ylim(0, ylim.value) +
    coord_cartesian(xlim = c(0, 1)) + 
    labs(title = "Selection proportion of genes selected more than once",
         x = "Selection frequency",
         y = "Number of genes") +
    theme(axis.text.x = element_text(size = 26, face = "bold"),
          axis.title.x = element_text(size = 28),
          axis.title.y = element_text(size = 28),
          axis.text.y = element_text(size = 30, face = "bold"),
          plot.subtitle = element_text(hjust = 0),
          plot.caption = element_text(size = 22, face = "bold"),
          panel.background = element_rect(fill = "#F6F6F6"),
          panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
          panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"),
          plot.title = element_blank(),
          legend.position = c(0.5, 0.8),
          legend.text = element_text(size = 28),    
   legend.title = element_text(size = 28) ,
   plot.margin = unit(c(0.6, 0.2, 0.2, 0.6), "cm")
    ) +
    scale_fill_manual(
      values = c("#b2a3e8", "#FF5733", "#FFFF66"),
      name = expression("LASSO (" * lambda[oracle] * "), n = 381")
    )
  
TP_1_LPLR_oracle <- nrow(df.genes.oracle[df.genes.oracle$freq == 1 & df.genes.oracle$status == "True genes ", ])
FD_1_LPLR_oracle <- nrow(df.genes.oracle[df.genes.oracle$freq == 1 & df.genes.oracle$status == "False discoveries ", ])
nb_selected_LPLR_oracle <- nrow(df.genes.oracle)
prop_TD_LPLR_oracle <- 100*nrow(df.genes.oracle[df.genes.oracle$status == "True genes ",])/nb_selected_LPLR_oracle
TP_all_LPLR_oracle <- nrow(df.genes.oracle[df.genes.oracle$status == "True genes ", ])

hist_KOPI_0.2 <- ggplot(data_0.2_KOPI, aes(x = freq, fill = status)) +
  geom_histogram(binwidth = 0.01, color = "black" ) +
  coord_cartesian(xlim = c(0, 1)) + 
  ylim(0, max_bin_count_KOPI_0.2) +
  labs(title = "Selection proportion of genes selected more than once",
       x = "Selection frequency",
       y = "Number of genes") +
 theme(axis.text.x = element_text(size = 26, face = "bold"),
        axis.title.x = element_text(size = 28),
        axis.title.y = element_text(size = 28),
        axis.text.y = element_text(size = 30, face = "bold"),
        plot.subtitle = element_text(hjust = 0),
        plot.caption = element_text(size = 22, face = "bold"),
        panel.background = element_rect(fill = "#F6F6F6"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"),
        plot.title = element_blank(),
        legend.position = c(0.5, 0.8),
        legend.text = element_text(size = 28),    
 legend.title = element_text(size = 28),
 plot.margin = unit(c(0.6, 0.2, 0.2, 0.6), "cm")
  ) +
  scale_fill_manual(values = c("#95b0b4", "#FF5733", "#FFFF66"), 
  name = "KOPI (q = 0.2), n = 113
  ") # Define colors for different statuses

hist_KOPI_0.2


TP_1_KOPI_0.2 <- nrow(data_0.2_KOPI[data_0.2_KOPI$freq == 1 & data_0.2_KOPI$status == "True genes ", ])
FD_1_KOPI_0.2 <- nrow(data_0.2_KOPI[data_0.2_KOPI$freq == 1 & data_0.2_KOPI$status == "False discoveries ", ])
nb_selected_KOPI_0.2 <- nrow(data_0.2_KOPI)
prop_TD_KOPI_0.2 <- 100*nrow(data_0.2_KOPI[data_0.2_KOPI$status == "True genes ",])/nb_selected_KOPI_0.2
TP_all_KOPI_0.2 <- nrow(data_0.2_KOPI[data_0.2_KOPI$status == "True genes ", ])


hist_KOPI_0.5 <- ggplot(data_0.5_KOPI, aes(x = freq, fill = status)) +
  geom_histogram(binwidth = 0.01, color = "black" ) +
  coord_cartesian(xlim = c(0, 1)) + 
  ylim(0, max_bin_count_KOPI_0.5) +
  labs(title = "Selection proportion of genes selected more than once",
       x = "Selection frequency",
       y = "Number of genes") +
 theme(axis.text.x = element_text(size = 26, face = "bold"),
        axis.title.x = element_text(size = 28),
        axis.title.y = element_text(size = 28),
        axis.text.y = element_text(size = 30, face = "bold"),
        plot.subtitle = element_text(hjust = 0),
        plot.caption = element_text(size = 24, face = "bold"),
        panel.background = element_rect(fill = "#F6F6F6"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"),
        plot.title = element_blank(),
        legend.position = c(0.5, 0.8),
        legend.text = element_text(size = 28),    
        legend.title = element_text(size = 28),
       plot.margin = unit(c(0.6, 0.2, 0.2, 0.6), "cm")
  ) +
  scale_fill_manual(values = c("#4e686b", "#FF5733", "#FFFF66"), name = "KOPI (q = 0.5), n = 520
                    ") # Define colors for different statuses

hist_KOPI_0.5


TP_1_KOPI_0.5 <- nrow(data_0.5_KOPI[data_0.5_KOPI$freq == 1 & data_0.5_KOPI$status == "True genes ", ])
FD_1_KOPI_0.5 <- nrow(data_0.5_KOPI[data_0.5_KOPI$freq == 1 & data_0.5_KOPI$status == "False discoveries ", ])
nb_selected_KOPI_0.5 <- nrow(data_0.5_KOPI)
prop_TD_KOPI_0.5 <- 100*nrow(data_0.5_KOPI[data_0.5_KOPI$status == "True genes ",])/nb_selected_KOPI_0.5
TP_all_KOPI_0.5 <- nrow(data_0.5_KOPI[data_0.5_KOPI$status == "True genes ", ])




data_0.2 <- data.frame(freq = prop_selection_0.2_0/100, status = as.factor(true_genes[ !prop_selection_0.2 == 0]))

hist_0.2 <- ggplot(data_0.2, aes(x = freq, fill = status)) +
  geom_histogram(binwidth = 0.01, color = "black") +
  coord_cartesian(xlim = c(0, 1)) + 
  ylim(0, max_bin_count_KO_0.2) +
  labs(title = "Selection proportion of genes selected more than once",
       x = "Selection frequency",
       y = "Number of genes") +
 theme(axis.text.x = element_text(size = 26, face = "bold"),
        axis.title.x = element_text(size = 28),
        axis.title.y = element_text(size = 28),
        axis.text.y = element_text(size = 30, face = "bold"),
        plot.subtitle = element_text(hjust = 0),
        plot.caption = element_text(size = 24, face = "bold"),
        panel.background = element_rect(fill = "#F6F6F6"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"),
        plot.title = element_blank(),
        legend.position = c(0.5, 0.8),
        legend.text = element_text(size = 28),    
        legend.title = element_text(size = 28),
       plot.margin = unit(c(0.6, 0.2, 0.2, 0.6), "cm")
  ) +
  scale_fill_manual(values = c("#17becf", "#FF5733", "#FFFF66"), 
name = "Vanilla KO (q = 0.2), n = 335
") # Define colors for different statuses

hist_0.2

TP_1_KO_0.2 <- nrow(data_0.2[data_0.2$freq == 1 & data_0.2$status == "True genes ", ])
FD_1_KO_0.2 <- nrow(data_0.2[data_0.2$freq == 1 & data_0.2$status == "False discoveries ", ])
nb_selected_KO_0.2 <- nrow(data_0.2)
prop_TD_KO_0.2 <- 100*nrow(data_0.2[data_0.2$status == "True genes ",])/nb_selected_KO_0.2
TP_all_KO_0.2 <- nrow(data_0.2[data_0.2$status == "True genes ", ])

data_0.5 <- data.frame(freq = prop_selection_0.5_0/100, status = as.factor(true_genes[ !prop_selection_0.5 == 0]))

hist_0.5 <- ggplot(data_0.5, aes(x = freq, fill = status)) +
  geom_histogram(binwidth = 0.01, color = "black") +
  coord_cartesian(xlim = c(0, 1)) + 
  ylim(0, max_bin_count_KO_0.5) +
  labs(title = "Selection proportion of genes selected more than once",
       x = "Selection frequency",
       y = "Number of genes") +
 theme(axis.text.x = element_text(size = 26, face = "bold"),
        axis.title.x = element_text(size = 28),
        axis.title.y = element_text(size = 28),
        axis.text.y = element_text(size = 30, face = "bold"),
        plot.subtitle = element_text(hjust = 0),
        plot.caption = element_text(size = 26, face = "bold"),
        panel.background = element_rect(fill = "#F6F6F6"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"),
        plot.title = element_blank(),
        legend.position = c(0.5, 0.8),
        legend.text = element_text(size = 28),    
        legend.title = element_text(size = 28),
       plot.margin = unit(c(0.6, 0.2, 0.2, 0.6), "cm")
  ) +
  scale_fill_manual(values = c("#008899", "#FF5733", "#FFFF66"), 
name = " Vanilla KO (q = 0.5), n = 1252
") 

hist_0.5

TP_1_KO_0.5 <- nrow(data_0.5[data_0.5$freq == 1 & data_0.5$status == "True genes ", ])
FD_1_KO_0.5 <- nrow(data_0.5[data_0.5$freq == 1 & data_0.5$status == "False discoveries ", ])
nb_selected_KO_0.5<- nrow(data_0.5)
prop_TD_KO_0.5 <- 100*nrow(data_0.2[data_0.5$status == "True genes ",])/nb_selected_KO_0.5
TP_all_KO_0.5 <- nrow(data_0.5[data_0.5$status == "True genes ", ])



graph_LPLR <- ggarrange(hist.genes, hist.genes.oracle, ncol = 2, labels = c("(a) ", "(b) "), common.legend = FALSE, font.label = list(size = 22)) 


graph_KO <- ggarrange(hist_0.2, hist_0.5, ncol = 2, labels = c("(c) ", "(d) "), common.legend = FALSE, font.label = list(size = 22)) 



graph_KOPI <- ggarrange(hist_KOPI_0.2, hist_KOPI_0.5, ncol = 2, labels = c("(e) ", "(f) "), common.legend = FALSE, font.label = list(size = 22)) 




combined_graph <- ggarrange(graph_LPLR, graph_KO, graph_KOPI,  ncol = 1, labels = NULL)


ggsave(file = "/home/julie/Documents/Paper_codes/Paper_graphs/Stability/Figures/Figure_3.png", plot = combined_graph, height = 24, width = 17)

```

```{r Data anlysis}

data_analysis <- replace(data_analysis, data_analysis == -Inf, 0)

mean(data_analysis[data_analysis$method == "LPLR (lambda.min)", 1])
mean(data_analysis[data_analysis$method == "LPLR (lambda.min)", 2])
mean(data_analysis[data_analysis$method == "LPLR (lambda.min)", 3])

mean(data_analysis[data_analysis$method == "LPLR (lambda.oracle)", 1])
mean(data_analysis[data_analysis$method == "LPLR (lambda.oracle)", 2])
mean(data_analysis[data_analysis$method == "LPLR (lambda.oracle)", 3])

mean(data_analysis[data_analysis$method == "KO 0.2", 1])
mean(data_analysis[data_analysis$method == "KO 0.2", 2])
mean(data_analysis[data_analysis$method == "KO 0.2", 3])

mean(data_analysis[data_analysis$method == "KO 0.5", 1])
mean(data_analysis[data_analysis$method == "KO 0.5", 2])
mean(data_analysis[data_analysis$method == "KO 0.5", 3])

mean(data_analysis[data_analysis$method == "KOPI 0.2", 1])
mean(data_analysis[data_analysis$method == "KOPI 0.2", 2])
mean(data_analysis[data_analysis$method == "KOPI 0.2", 3])

mean(data_analysis[data_analysis$method == "KOPI 0.5", 1])
mean(data_analysis[data_analysis$method == "KOPI 0.5", 2])
mean(data_analysis[data_analysis$method == "KOPI 0.5", 3])
```





